Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed Quasars

### 2020-05-26 manuscript/manuscript.tex
Push to Overleaf for the final check by TT

% Abstract of the paper
\begin{abstract}
  One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution. Strong lensing magnification effectively increases instrumental resolution and thus helps to address this challenge. In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope}(\hst) imaging, using the \pink{lens modelling code} \lenstronomy\ to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models. 
  \mbh\ are estimated from broad emission lines using standard methods. Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolves over cosmic time.  At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN. However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and they may become a key diagnostic of black hole and galaxy co-evolution. 
\end{abstract}

@@

A powerful way to understand the origin of the correlations is to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}. Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations in the redshift range $1.2<z<1.7$ using multi-color Wide Field Camera 3 (WFC3) \hst\ imaging. Combining the new sample with published samples in both local and intermediate \pink{(i.e., $0.35<z\lesssim1.2$)} redshift ranges, D20 strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy. In a follow-up paper, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}. The observed tightness of the  scaling relations at high redshift is consistent with the hypothesis that AGN feedback drives the scaling correlations, and disfavors the hypothesis of the correlations being purely stochastic in nature. 
% , a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.

@@

In this work, we expand the measurements of the \mbh-\mstar\ relation using the full sample of eight lensed AGN introduced by \citet{Ding2017a}.  In order to take advantage of the excellent quality of the data, we develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs. We adopt a set of extended modelling choices to \pink{estimate the host property uncertainty level and} ensure the accuracy of our measurements. We compare the inference of our new measurements to the ones that have been modelled by the H0LiCOW collaboration to make the cross-check. To obtain an accurate inference of stellar mass, we utilize the multi-band imaging data taken with the \hst\ to obtain the color information for 3/8 of our targets. \pink{We assume a typical stellar population for the rest 5/8 of the sample.} Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20. Given the similar redshift range, the high data quality, and consistent state-of-the-art techniques, this sample of lensed AGN provides an excellent verification of the D20 results.

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and the BH masses. In Section~\ref{sec:lens_model}, we describe our approach designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}. Discussion and conclusions are drawn in Sections~\ref{sec:diss} and~\ref{sec:con}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, \pink{to compute the luminosity distance and estimate the host absolute brightness}. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the sample, to be consistent with D20.

@@

Based on the observational data of these eight systems, \citet{Ding2017a} performed an extensive and realistic simulation exercise using the \hst\ image data and confirmed that the source reconstruction using the lens modelling technique is trustworthy. We summarize the information for the eight systems, including \pink{their redshift, data properties, and references} in Table~\ref{data_set}.
Besides the imaging data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems. As we show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to improve the accuracy of the estimate of \mstar.

The sample of lensed AGN is too limited in size to constrain evolution by itself. Therefore, we use it primarily to verify the results of D20.  The D20 sample includes 32 AGN measurements in the redshift range $1.2<z<1.9$. \pink{They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}.} It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
\pink{where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:}
%
$a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\} ($\AA$).
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, \pink{based on \Mgii}. The \mbh\ measurements, together with the properties of the board-line, are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of \mbh\ estimates, based on equation~\eqref{recipe}.}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{cccccc}
        \hline
Object ID & Line(s) & FWHM & log($L_\lambda$) & $\log$\mbh & ref.  \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 & (1) \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 & (1)\\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 & (1) \\
SDSS1206 & \Mgii & 5632 & 45.01 & 8.77 & (2) \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 & (3) \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 & (1) \\
HS2209 & \Mgii & 3245 & 45.71 & 8.75 & here  \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 & (1) \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
\small
\item Note: $-$ The broad line properties.\\ %For HS2209, the properties are derived in this work using the same approach as~\citet{Sluse2012}.
Reference: (1)~\citet{Sluse2012}, (2)~\citet{Shen2011}, (3)~\citet{Peng2006}.\\
%$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect {\bf [TT: how about the others?].}
\end{tablenotes}  
%\end{threeparttable}
\end{table}

\section{surface photometry inference}\label{sec:lens_model}
%
In this section, we describe how we derived surface photometry of the lensed galaxies taking lensing effects into account. Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project. The goal of those models was strong lens time-delay cosmography~\citep{Refsdal1966, Treu2016}, and the reconstruction of the host galaxy light \pink{(via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003})} was a byproduct. \citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to \pink{measure the host properties as the non-lensed AGN case}.
% mimic what is done in non-lensed AGN.

@@

We follow the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolutions are listed in Table~\ref{data_set}. We then adopt the {\sc Photutils}~\citep{photutils} Python package to model the global background light in 2-D, based on the \texttt{SExtractor} algorithm. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-\pink{middle} panel in each subplot in Figure~\ref{fig:image_inference}.

@@

We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task. Building on D20, we adopt a set of  modelling choices and fit each system multiple times. Then, we do a statistical analysis of the measurements, and apply a weighting algorithm to derive the final inference and estimate the uncertainty level. The modelling choices that we consider include the follows.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF guess for the fit.
\item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
\item To calculate the ray tracing under a higher resolution grid, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, \pink{especially with our simplified model of the host light distribution}. To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
\end{enumerate}

In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ \pink{(i.e., $2$ by (ii) $\times~2$ by (iii) $\times~3$ by (iv)) fits}. After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value. Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20. The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
\end{eqnarray} 
Then, the results for {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

Our approach uses the relative goodness of fit and ensures that at least 8 sets of best fits are used to estimate the range of systematic uncertainties. \pink{Note that the slope of the mass profile of the deflector is fixed in each fit, and that the statistical uncertainty is much smaller than the systematic one.}

@@

We also compare our measurement to the previous reconstructions by \citet{Ding2017b}. Based on the reconstructions by~\citet{Suyu2013}, the inference of the host magnitudes by~\citet{Ding2017b} are $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$. The results are in excellent agreement with our inferred bulge magnitude ($21.80\pm0.21$)   shown in Table~\ref{tab:host_measure}. However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}. This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein). \pink{Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the source plane reconstructions by~\citet{Suyu2013}, based on pixellated grid in the source plane. We checked that finite grid effects did not introduce any substantial difference. As a sanity check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (this paper) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies. While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.

\subsubsection{WFI2033}
WFI2033 is the last quadruply lensed system in our sample whose lens model has been previously investigated \citep{Rusu2019}. There is a satellite galaxy in the north. However, as noted by~\citet{Rusu2019}, the satellite galaxy has much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using a \sersic\ model. We select a total of 8 initial PSF stars to model this system.

@@

\pink{It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data. Their inferred host light is $20.14\pm0.30$ mag in Vega system, which is also consistent to our inference ($20.00\pm0.15$ mag in Vega).}
%zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
%HE1104 mag:  21.25 (AB)  --> 20.00 (Vega)

@@

{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W. The multi-band imaging data provides us with the opportunity to estimate the host color and improve the stellar mass estimate. We adopted the lensing modelling approach described in Section~\ref{sec:photometry} to infer the host photometry through the F814W and F555W bands. Based on the three band host magnitudes, we find that a 1.5~Gyr age and solar metallicity stellar population provides a good match to the color. More detailed information is presented in Appendix~\ref{app:HE0435}.
%Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy. Thus, we infer the color of the lensed arcs in the image plane. Based a their magnitudes in three bands, we find a 1.5 Gyr stellar population with solar metallicity could well match this color. More detailed information is presented in Appendix~\ref{app:HE0435}.}

{\bf RXJ1131} ~ The host galaxy of RXJ1131 is lensed to a very extended arc in the image plane. The spectral energy distribution of the arc can be directly inferred in the image plane, since lensing is achromatic. Based on the \hst\ imaging data through the three filters F814W and F555W and F160W, we adopt the SED estimated by~\citet{Ding2017b} with stellar populations of 3 Gyr and 1.5 Gyr (solar metallicity) for its bulge and disk, respectively. \pink{We refer the interested reader to that paper for more details.}

@@

\section*{Acknowledgements}
\pink{We are grateful to Frederic Courbin, Leon Koopmans for useful comments
and suggestions that improved this manuscript.}

>>>>

% Abstract of the paper
\begin{abstract}
One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution. Strong lensing magnification effectively increases instrumental resolution and thus helps to address this challenge. In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope} (\hst) imaging, using the lens modelling code \lenstronomy\ to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models.  \mbh\ are estimated from broad emission lines using standard methods. Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolves over cosmic time.  At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN. However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and they may become a key diagnostic of black hole and galaxy co-evolution. 
\end{abstract}

@@

A powerful way to understand the origin of the correlations is to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}. Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations in the redshift range $1.2<z<1.7$ using multi-color Wide Field Camera 3 (WFC3) \hst\ imaging. Combining the new sample with published samples in both local and intermediate (i.e., $0.35<z\lesssim1.2$) redshift ranges, D20 strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy. In a follow-up paper, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}. The observed tightness of the  scaling relations at high redshift is consistent with the hypothesis that AGN feedback drives the scaling correlations, and disfavors the hypothesis of the correlations being purely stochastic in nature. 
% , a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.

@@

In this work, we expand the measurements of the \mbh-\mstar\ relation using the full sample of eight lensed AGN introduced by \citet{Ding2017a}.  In order to take advantage of the excellent quality of the data, we develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs. We adopt a set of extended modelling choices to estimate the host property uncertainty level and ensure the accuracy of our measurements. We compare the inference of our new measurements to the ones that have been modelled by the H0LiCOW collaboration to make the cross-check. To obtain an accurate inference of stellar mass, we utilize the multi-band imaging data taken with the \hst\ to obtain the color information for 3/8 of our targets. We assume a typical stellar population for the rest 5/8 of the sample. Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20. Given the similar redshift range, the high data quality, and consistent state-of-the-art techniques, this sample of lensed AGN provides an excellent verification of the D20 results.

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and the BH masses. In Section~\ref{sec:lens_model}, we describe our approach designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}. Discussion and conclusions are drawn in Sections~\ref{sec:diss} and~\ref{sec:con}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, to compute the luminosity distance and estimate the host absolute brightness. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the sample, to be consistent with D20.

@@

Based on the observational data of these eight systems, \citet{Ding2017a} performed an extensive and realistic simulation exercise using the \hst\ image data and confirmed that the source reconstruction using the lens modelling technique is trustworthy. We summarize the information for the eight systems, including their redshift, data properties, and references in Table~\ref{data_set}.
Besides the imaging data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems. As we show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to improve the accuracy of the estimate of \mstar.

The sample of lensed AGN is too limited in size to constrain evolution by itself. Therefore, we use it primarily to verify the results of D20.  The D20 sample includes 32 AGN measurements in the redshift range $1.2<z<1.9$. They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}. It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:
%
$a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}~(\AA).
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, based on \Mgii.
\pink{The magnification correction on these systems are not self-consistent, which could introduce some systematics on the intrinsic value the $\log(L_\lambda)$. However, these errors only have limited effect on the \mbh\ estimations, given that the virial relations depend on roughly the square root of the $\log(L_\lambda)$.}
The \mbh\ measurements, together with the properties of the broad-line, are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of \mbh\ estimates, based on equation~\eqref{recipe}.}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{cccccc}
        \hline
Object ID & Line(s) & FWHM & log($L_\lambda$) & $\log$\mbh & ref.  \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 & (1) \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 & (1)\\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 & (1) \\
SDSS1206 & \Mgii & 5632 & 45.01 & 8.60 & (2) \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 & (3) \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 & (1) \\
HS2209 & \Mgii & 3245 & 45.71 & 8.45 & here  \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 & (1) \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
\small
\item Note: $-$ The broad line properties.\\ %For HS2209, the properties are derived in this work using the same approach as~\citet{Sluse2012}.
Reference: (1)~\citet{Sluse2012}, (2)~\citet{Shen2011}, (3)~\citet{Peng2006}.\\
%$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect {\bf [TT: how about the others?].}
\end{tablenotes}  
%\end{threeparttable}
\end{table}

\section{surface photometry inference}\label{sec:lens_model}
%
In this section, we describe how we derived surface photometry of the lensed galaxies taking lensing effects into account. Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project. The goal of those models was strong lens time-delay cosmography~\citep{Refsdal1966, Treu2016}, and the reconstruction of the host galaxy light (via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003}) was a byproduct. \citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to measure the host properties as the non-lensed AGN case.
% mimic what is done in non-lensed AGN.

@@

We follow the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolutions are listed in Table~\ref{data_set}. We then adopt the {\sc Photutils}~\citep{photutils} Python package to model the global background light in 2-D, based on the \texttt{SExtractor} algorithm. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-middle panel in each subplot in Figure~\ref{fig:image_inference}.

@@

We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task, \pink{in which we use the optimization algorithm based on the ``particle swarm optimizer''}. Building on D20, we adopt a set of  modelling choices and fit each system multiple times. Then, we do a statistical analysis of the measurements, and apply a weighting algorithm to derive the final inference and estimate the uncertainty level. The modelling choices that we consider include the follows.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF guess for the fit.
\item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boosting the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~performing the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
\item To calculate the ray tracing under a higher resolution grid \pink{relative to the pixel sizes in the image plane}, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, especially with our simplified model of the host light distribution. To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Koopmans2006, Auger2010}.
\end{enumerate}

In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2$ by (ii) $\times~2$ by (iii) $\times~3$ by (iv)) fits. After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value. Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20. \pink{The degrees of freedom is the same for each of the model, which validates this weighting process.} The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{\rm best} ^2 )}{2 \chi_{\rm best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{\rm best} ^2 }{2 \chi_{\rm best} ^2} = 2.
\end{eqnarray} 
Then, the results for {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

Our approach uses the relative goodness of fit and ensures that at least 8 sets of best fits are used to estimate the range of systematic uncertainties. Note that the slope of the mass profile of the deflector is fixed in each fit, and that the statistical uncertainty is much smaller than the systematic one.

@@

We also compare our measurement to the previous reconstructions by \citet{Ding2017b}. Based on the reconstructions by~\citet{Suyu2013}, the inference of the host magnitudes by~\citet{Ding2017b} are $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$. The results are in excellent agreement with our inferred bulge magnitude ($21.80\pm0.21$)   shown in Table~\ref{tab:host_measure}. However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}. This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein). Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the \pink{pixellated source reconstructed by~\citet{Suyu2013} in the source plane.} We checked that finite grid effects did not introduce any substantial difference. As a sanity check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (this paper) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}. The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies. While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.

\subsubsection{WFI2033}
WFI2033 is the last quadruply lensed system in our sample whose lens model has been previously investigated \citep{Rusu2019}. There is a satellite galaxy in the north. However, the satellite galaxy has much smaller mass than the main deflector. \pink{In addition, there is a galaxy located in the west which could has an impact on the modelling, which also has small effect on the total macro-magnification $(<10\%)$. Thus, we ignore their influence on the magnification but only fit the light of the satellite galaxy} using a \sersic\ model. 
We select a total of 8 initial PSF stars to model this system.

@@

It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data. Their inferred host light is $20.14\pm0.30$ mag in Vega system, which is also consistent to our inference ($20.00\pm0.15$ mag in Vega).
%zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
%HE1104 mag:  21.25 (AB)  --> 20.00 (Vega)

@@

{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W. The multi-band imaging data provides us with the opportunity to estimate the host color and improve the stellar mass estimate. We adopted the lensing modelling approach described in Section~\ref{sec:photometry} to infer the host photometry through the F814W and F555W bands. Based on the three band host magnitudes, we find that a 1.5~Gyr age and solar metallicity stellar population provides a good match to the color. More detailed information is presented in Appendix~\ref{app:HE0435}.

{\bf RXJ1131} ~ The host galaxy of RXJ1131 is lensed to a very extended arc in the image plane. The spectral energy distribution of the arc can be directly inferred in the image plane, since lensing is achromatic. Based on the \hst\ imaging data through the three filters F814W and F555W and F160W, we adopt the SED estimated by~\citet{Ding2017b} with stellar populations of 3 Gyr and 1.5 Gyr (solar metallicity) for its bulge and disk, respectively. We refer the interested reader to that paper for more details.

@@

\section*{Acknowledgements}
We are grateful to Frederic Courbin, Leon Koopmans for useful comments
and suggestions that improved this manuscript.
